Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-14 WRITEUP/ms.tex
fleshed out a bit more

\begin{abstract}
We study the dynamical properties of molecular cloud complexes (MC) in a prototypical galaxy (\flower) 
at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
%
We identify MCs using H$_2$ density, and compare their masses, sizes, velocity dispersions, gas surface densities, and virial parameters ($\alpha_{\rm vir}$) with those observed in nearby and \z$\sim$\,2 galaxies.
%
The MCs span a mass range of $10^{6.5-9}$\,\Msun and a size range of $R\lesssim200$\,pc. Their velocity dispersions and gas surface densities are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We compute the effective two-component Toomre $Q_{\rm eff}$ parameter (gas and stars) to examine regions that are 
gravitationally unstable.
%
We further perform virial analysis, which is accessible to observations, to examine regions that are likely 
to undergo collapse. Our analysis indicates that MCs in the main disk of \flower are unbound, but its 
substructures have lower virial parameters and Toomre $Q_{\rm eff}$, which is consistent 
with the notion that collapsing structures occur within globally stable structures.
%
We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback 
compared to \flower. Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the 
higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\AP{For some plots, still the old versions are the ones available. It might still be overleaf fault. An option would be to have a clean new overleaf document; pros: probably the compilation will be faster and the service less buggy (e.g. selecting every time the main manuscript file, files are actually uploaded, etc) and thus more convenient to use; cons: it will not be syncronized with the repo}

@@

In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}, or the Toomre $Q$ parameter (\AP{i would put this parenthesis as a note later on, i.e. close to \Eq{q_eff}} or the proxy, circular velocity to dispersion ratio; $v_{\rm circ}/\sigma$; e.g., \citealt{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}).
% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
%
% from linear analysis
For {\it axisymmetric} mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk of 
finite thickness $h$ is described by 
\begin{equation}
\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2\,,
\label{eqn:3Ddisp}
\end{equation}
where $k$ is the wavenumber and $\kappa$ is the epicyclic frequency, defined as:
\begin{equation}
\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right)\,,
\label{eqn:kappa}
\end{equation}
\citep{Romeo92a}.
The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and the third term describes internal pressure support. Then the Toomre-Q parameter can be defined as \citep{Toomre64a}:
\begin{equation}
Q_{\rm gas}\equiv\frac{\sigma\kappa}{\pi G \Sigma}\,.
\label{eqn:Q}
\end{equation}
In the thin disk approximation ($kh\ll1$), the solution of \Eq{3Ddisp} is unstable for scales $k$ such that $Q < 1$ (or equivalently $\omega^2 < 0$). Physically, this situation happens when local gravitational instability 
overcomes support from pressure and rotation, allowing fragmentation and collapse to happen.
% but further evolution depends on their EOS. (e.g., instability impose by angular momentum from gas accretion from the cosmic web and satellite galaxies and stellar feedback).
% Note that fragmentation is expected to happen at critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$, which is greater than the typical size of  GMCs. It should be clear that the instability sets the scales for fragmentation, but star-forming GMCs are the collapsing, denser, and cooler molecular structures on even smaller scales. The fragmented structures thus correspond to regions where $Q\lesssim1.
Similarly, for a collisionless fluid -- as an ensamble of stars -- the Toomre $Q$ parameter is defined by \citep{Toomre64a}:
\begin{equation}
Q_{\star} \equiv\frac{\sigma\kappa}{3.36 G \Sigma}\,.
\end{equation}

In our stability analysis, we account for a non-negligible disk thickness and for the combined effect of gas and stars; this is done adopting the approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.][see also \citealt{Inoue16a}]{Romeo11a}.
%
The effect of disk thickness modify the $Q$ parameter for gas/star by accounting for the vertical velocity dispersion:
\begin{equation}
T_{x} = \left\{
		\begin{array}{lccr}
			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [1.25em]
			{\displaystyle 1 + 0.6\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}        & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r 
\\
		\end{array}
	\right.
\end{equation}
and
\begin{equation}
Q^{\rm thick}_{x} = T_{x} Q\,,
\end{equation}
with $x$ indicating either gas or stars.
%
The combined effect of gas and stars can then be account by writing
\begin{equation}\label{eqn:q_eff}
%Q^{-1}_{\rm eff} =  \left\{
%				\begin{array}{lccr}
%					     {\displaystyle\frac{w}{T_{\rm star} Q_{\star}} + \frac{1}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\star} \geq T_{\rm gas} Q_{\rm gas} \\ [0.75em]
%                                               {\displaystyle\frac{1}{T_{\rm star} Q_{\star}} + \frac{w}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\star} \leq T_{\rm gas} Q_{\rm gas} \\				
%				\end{array} 
%			    \right.
Q^{-1}_{\rm eff} =  \left\{
				\begin{array}{lccr}
					     {\displaystyle\frac{w}{Q^{\rm thick}_{\rm star}} + \frac{1}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ }  Q^{\rm thick}_{\rm star} \geq Q^{\rm thick}_{\rm gas} \\ [0.75em]
                                               {\displaystyle\frac{1}{Q^{\rm thick}_{\rm star}} + \frac{w}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ } Q^{\rm thick}_{\rm star} \leq Q^{\rm thick}_{\rm gas} \\				
				\end{array} 
			    \right.
\end{equation}
where the relative weight $w$ is defined as:
\begin{equation}
w\equiv\frac{2 \sigma_{\star} \sigma_{\rm gas}}{\sigma_{\star}^2 + \sigma_{\rm gas}^2},
\end{equation}
\AP{symbol already used for internal enrgy in \Eq{virial_th_general}; do we already need the virial theorem derivation?}
\DL{this is small $w$. Whether or not we need the Larson's relation stuff, I think those eqns there help understand the motivation 
behind relating aa with bb and bb and cc, etc, in the Larson's relations?}

For the purpose of this work, we present Toomre $Q$ maps in \Sec{results} and discuss the importance of support from galactic rotation and shear against axisymmetric perturbations in \Sec{origin}.

@@

\begin{figure*}
\centering
\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_larsons.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-larsons-highncut.png}
\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_alphavir.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16-28_PVE.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-PVE-highncut.png}
\caption{
\AP{evolutionary stage (function of sfr), different cuts (left/right)}\AP{similarly to the previous figure for different cuts; we might visually distinguish the points different color codes for the SFR and $n_{cut}$}
\label{fig:alpha16-28}}
\end{figure*}

@@

The high pressure observed in \flower is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
For instance, in local ULIRGs, they are likely form by shock compression and cloud-cloud collision after large amount of gas from the pair of progenitor galaxies are being funneled toward the central region \citep{Tan00a, Wu18a}.
% Tasker09a
On the other hand, the highly turbulent structures of \flower likely result from constant cold gas accretion onto the entire galaxy \AP{i do not fully grasp the following point} (without requiring gas to be funneled into the central region).
This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also result from resolution limit where the true physical scales of MCs in $z$\,\ssim2 galaxies could be smaller in reality.
%
The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render
the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which is 
consistent with the high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.

@@

 \DL{should probably move to somwehere later in this sec}
Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Qeff} 
(see also \Fig{h2density} for example of MCs identified in this evolutionary stage of \flower
using different $n_{\rm cut}$). Fragmentation are expected in regions of low Toomre $Q$ values.
Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the 
stellar component play an important role in 
governing the stability of the MCs against $m$\eq0 perturbations.
This can be understood since stars in \flower dominates the central part of the galaxy in mass, 
so their gravitational potential provides a non-negligible contribution to the stability. 
Similarly, contribution from the thickness of the disk is important in \flower since its disk is not thin (with a 
scale height to radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15) and since \flower is more of a warped disk.
That is, some MCs are found in regions of $Q_{\rm gas}$\ssim1, which would suggest that they are gravitationally unstable;
however, when including the stabilizing effects due to its stellar potential and the 
thickness of its disk (via $\sigma_z$), some of these MCs are consistent with $Q_{\rm eff} > 1$.
This highlights the importance of accounting for stellar contribution and disk thickness when examining the stability of 
molecular gas structures, especially in the relatively evolved and enriched systems at high redshifts 
that are preferentially being imaged at high resolution with ALMA. One should be caution when interpreting results
based on gas-only Toomre $Q$ analysis.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.92\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_2.0}.pdf}
\includegraphics[trim=0 0 0 65, clip, width=0.95\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_0.8}.pdf}
\caption{
Toomre $Q$ maps derived from the 
central $r$\eq2\,kpc (top row) and $r$\eq0.8\,kpc (bottom row) of \flower.
Gas-only $Q_{\rm gas}$ are shown in the left panels and stellar-only $Q_\star$ are shown in the middle panels.
Maps of the effective two-component Toomre $Q_{\rm eff}$ parameter are shown in the right panels. 
All maps are projected onto the $xy$-plane.
Positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
A smoothing length of 30\,pc has been applied to the maps.
A divergent colormap is used for the Toomre $Q$ maps to facilitate 
identification of regions above and below $\log{Q}$\eq0.
Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ 
are likely gravitationally unstable.
\label{fig:Qeff}}
\end{figure*}

>>>>

\begin{abstract}
We study the dynamical properties of molecular cloud complexes (MC) in a prototypical galaxy (\flower)
at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
%
We identify MCs using H$_2$ density, and compare their masses, sizes, velocity dispersions, gas surface densities, and virial parameters ($\alpha_{\rm vir}$) with those observed in nearby and \z$\sim$\,2 galaxies.
%
The MCs span a mass range of $10^{6.5-9}$\,\Msun and a size range of $R\lesssim200$\,pc. Their velocity dispersions and gas surface densities are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We compute the effective two-component Toomre $Q_{\rm eff}$ parameter (gas and stars) to examine regions that are
gravitationally unstable.
%
We further perform virial analysis, which is accessible to observations, to examine regions that are likely
to undergo collapse. Our analysis indicates that MCs in the main disk of \flower are unbound, but its
substructures have lower virial parameters and Toomre $Q_{\rm eff}$, which is consistent
with the notion that collapsing structures occur within globally stable structures.
%
Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\AP{For some plots, still the old versions are the ones available. It might still be overleaf fault. An option would be to have a clean new overleaf document; pros: probably the compilation will be faster and the service less buggy (e.g., selecting every time the main manuscript file, files are actually uploaded, etc) and thus more convenient to use; cons: it will not be syncronized with the repo}

@@

In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}, or the Toomre $Q$ parameter (\AP{i would put this parenthesis as a note later on, i.e. close to \Eq{q_eff}} or the proxy, circular velocity to dispersion ratio; $v_{\rm circ}/\sigma$; e.g., \citealt{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}).
% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
%
% from linear analysis
For {\it axisymmetric} mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk of
finite thickness $h$ is described by
\begin{equation}
\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2\,,
\label{eqn:3Ddisp}
\end{equation}
where $k$ is the wavenumber and $\kappa$ is the epicyclic frequency, defined as:
\begin{equation}
\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right)\,,
\label{eqn:kappa}
\end{equation}
\citep{Romeo92a}.
The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and the third term describes internal pressure support. The Toomre-Q parameter can be defined as \citep{Toomre64a}:
\begin{equation}
Q_{\rm gas}\equiv\frac{\sigma\kappa}{\pi G \Sigma}\,.
\label{eqn:Q}
\end{equation}
In the thin disk approximation ($kh\ll1$), the solution of \Eq{3Ddisp} is unstable for scales $k$ such that 
$Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$). Physically, this situation happens when local gravitational instability
overcomes support from pressure and rotation, allowing fragmentation and collapse to happen.
Similarly, for a collisionless fluid --- as an ensemble of stars --- the Toomre $Q$ parameter is defined by \citep{Toomre64a}:
\begin{equation}
Q_{\star} \equiv\frac{\sigma\kappa}{3.36 G \Sigma}\,.
\end{equation}

In our stability analysis, we account for a non-negligible disk thickness and for the combined effect of gas and stars; this is done adopting the approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
%
The effect of disk thickness modify the $Q$ parameter for gas/star by accounting for the vertical velocity dispersion:
\begin{equation}
T_{x} = \left\{
		\begin{array}{lccr}
			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [1.25em]
			{\displaystyle 1 + 0.6\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}        & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r
\\
		\end{array}
	\right.
\end{equation}
and
\begin{equation}
Q^{\rm thick}_{x} = T_{x} Q\,,
\end{equation}
with $x$ indicating either gas or stars.
% Note that w/ thickness, there's the a self-gravity dilution term in the dispersion relation, which in effect reduceds the surface gravity in the vertical direction. As such, it is easier to be stable against gravitaional instability. Thus, the criterion for instability $Q$ is reduced.
%
The combined effect of gas and stars can then be accounted for by writing
\begin{equation}\label{eqn:q_eff}
Q^{-1}_{\rm eff} =  \left\{
				\begin{array}{lccr}
					     {\displaystyle\frac{w}{Q^{\rm thick}_{\rm star}} + \frac{1}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ }  Q^{\rm thick}_{\rm star} \geq Q^{\rm thick}_{\rm gas} \\ [0.75em]
                                               {\displaystyle\frac{1}{Q^{\rm thick}_{\rm star}} + \frac{w}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ } Q^{\rm thick}_{\rm star} \leq Q^{\rm thick}_{\rm gas} \\
				\end{array}
			    \right.
\end{equation}
where the relative weight $w$ is defined as:
\begin{equation}
w\equiv\frac{2 \sigma_{\star} \sigma_{\rm gas}}{\sigma_{\star}^2 + \sigma_{\rm gas}^2},
\end{equation}
Conceptually, the thickness of a disk reduces the gravity in the vertical direction, thereby making 
a system easier to obtain stability, and thus, lowering the criterion of the critical Toomre 
$Q_{\rm crit}$ from $\simeq$\,1 to 
0.67 \citep{Goldreich65a}. On the other hand, including the contribution of the stellar 
component promotes gravitational instability, and thus, increasing the criterion of the Toomre $Q_{\rm crit}$.
unless it is dynamically hot to ``compensate''.  
As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2
\AP{symbol already used for internal enrgy in \Eq{virial_th_general}; do we already need the virial theorem derivation?}
\DL{this is small $w$. Whether or not we need the Larson's relation stuff, I think those eqns there help understand the motivation
behind relating aa with bb and bb and cc, etc, in the Larson's relations?}

@@

\begin{figure*}
\centering
\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_larsons.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-larsons-highncut.png}
\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_alphavir.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16-28_PVE.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-PVE-highncut.png}
\caption{
Same as \Fig{larsons_single}, except star symbols are showing MCs identified across all evolutionary 
stages traced in our simulation, which are color-coded by the SFR of \flower in those stages. 
Left panels show MCs identified using a low $n_{\rm cut}$ \DL{check how low?} 
and right panels show MCs identified using a high $n_{\rm cut}$ \DL{check how high?}.
\label{fig:alpha16-28}}
\end{figure*}

@@

The high pressure observed in \flower is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
For instance, in local ULIRGs, they are likely form by shock compression and cloud-cloud collision after large amount of gas from the pair of progenitor galaxies are being funneled toward the central region \citep{Tan00a, Wu18a}.
% Tasker09a
On the other hand, the highly turbulent structures of \flower likely result from constant cold gas accretion onto the entire galaxy \AP{i do not fully grasp the following point} \DL{doesn't it take a long time for gas to lose angular 
momentum to fall onto the central region of a galaxy? Given turbulent it is across the entire galaxy \Fig{sigma}, 
isn't more conceivable that cold gas accretion is the dominant reason to the turbulent structures in \flower?} 
(without requiring gas to be funneled into the central region).
This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also result from resolution limit where the true physical scales of MCs in $z$\,\ssim2 galaxies could be smaller in reality.
%
The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render
the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which is
consistent with the high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.

@@

 \DL{should probably move to somwehere later in this sec}
Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Qeff}
(see also \Fig{h2density} for example of MCs identified in this evolutionary stage of \flower
using different $n_{\rm cut}$). Fragmentation are expected in regions of low Toomre $Q$ values.
Close resemblance of the $Q_{\star}$ and $Q_{\rm eff}$ maps (especially in the central region of \flower)
indicates that contributions from the stellar component play an important role in
governing the stability of the MCs against $m$\eq0 perturbations.
This can be understood since stars in \flower dominates the central part of the galaxy in mass,
so their gravitational potential provides a non-negligible contribution to the instability.
Similarly, contribution from the thickness of the disk is important in \flower since its disk is not thin (with a
scale height to radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15) and since \flower is more of a warped disk. That is, some MCs are found in regions of $Q_{\rm gas}$\ssim1, 
which would suggest that they are gravitationally unstable;
however, when including the effects due to its stellar potential and the
thickness of its disk (via $\sigma_z$), some of these MCs are consistent with $Q_{\rm eff} > 1$.
This highlights the importance of accounting for stellar contribution and disk thickness 
when examining the stability of
molecular gas structures, especially in the relatively evolved and enriched systems at high redshifts
that are preferentially being imaged at high resolution with ALMA. 
One should be caution when interpreting results based on gas-only Toomre $Q$ analysis.
In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with 
both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. 
Notably, these are the more gas-rich regions (see \Fig{sigma}).

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.92\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_2.0}.pdf}
\includegraphics[trim=0 0 0 65, clip, width=0.95\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_0.8}.pdf}
\caption{
Toomre $Q$ maps derived from the
central $r$\eq2\,kpc (top row) and $r$\eq0.8\,kpc (bottom row) of \flower.
Gas-only $Q_{\rm gas}$ are shown in the left panels and stellar-only $Q_\star$ are shown in the middle panels.
Maps of the effective two-component Toomre $Q_{\rm eff}$ parameter are shown in the right panels.
All maps are projected onto the $xy$-plane.
Positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
A smoothing length of 30\,pc has been applied to the maps.
A divergent colormap is used for the Toomre $Q$ maps to facilitate
identification of regions above and below $\log{Q}$\eq0.
Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$
are likely gravitationally unstable.
Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the central region of \flower 
indicates that stellar component plays an important role in governing the stability of the MCs against $m=0$  perturbations, highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
\label{fig:Qeff}}
\end{figure*}
